A game-theory modeling approach to utility and strength of interactions dynamics in biomedical research social networks

### 2016-11-09 manuscript_3.tex
include images in path

}\\

@@

\begin{figure} [h!]
\centering
\includegraphics[scale=0.5]{Fosiss_GC_final.png}
\caption{Bioemdical research collaboration network (FOSISS) giant component.}\label{Fosiss_GC}
\end{figure}

@@

\includegraphics[scale=0.28]{erdos_dc_nus_1.png} & \includegraphics[scale=0.28]{watts_dc_nus_1.png} \\
\includegraphics[scale=0.28]{barabasi_dc_nus_1.png} & \includegraphics[scale=0.28]{fosiss_dc_nus_1.png}
\end{tabular}
\caption{Proportion of cooperators as a function of carrying capacity and time.}\label{CD}
\end{figure}

@@

\includegraphics[scale=0.28]{erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{watts_fitness_nus_1.png} \\
\includegraphics[scale=0.28]{barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{fosiss_fitness_nus_1.png}
\end{tabular}
\caption{Utility $U$ dynamics as a function of carrying capacity $\nu$ and time.}\label{fitness}
\end{figure}

@@

\includegraphics[scale=0.28]{erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{watts_trust_nus_1.png} \\
\includegraphics[scale=0.28]{barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{fosiss_trust_nus_1.png}
\end{tabular}
\caption{Strength of interactions $w$ dynamics as a function of carrying capacity $\nu$ and time.}\label{trust}
\end{figure}

@@

\includegraphics[scale=0.28]{erdos_state_nus.png} & \includegraphics[scale=0.28]{watts_state_nus.png} \\
\includegraphics[scale=0.28]{barabasi_state_nus.png} & \includegraphics[scale=0.28]{fosiss_state_nus.png}
\end{tabular}
\caption{Shifting population between cooperators and defectors as a function of
  carrying capacity $\nu$ and time.}\label{state} 
\end{figure}

@@

\includegraphics[scale=0.28]{erdos_fitness.png} & 
\includegraphics[scale=0.28]{watts_fitness.png} \\
\includegraphics[scale=0.28]{barabasi_fitness.png} & 
\includegraphics[scale=0.28]{fosiss_fitness.png}
\end{tabular}
\caption{Utility distribution on different topologies. A. Random,
  Erd\"{o}s-R\'enyi network displays a normal-like
  distribution. B. Watts-Strogatz network utility distribution is highly skewed
  to the right. C. Barab\'asi-Albert network. Utility is distributed highly
  skewed to the left. D. FOSISS, biomedical researchers collaboration network
  distribution of utility resembles to Barab\'asi-Albert
  network.}\label{histo_fitness} 
\end{figure}

@@

\includegraphics[scale=0.28]{erdos_trust.png} & 
\includegraphics[scale=0.28]{watts_trust.png} \\
\includegraphics[scale=0.28]{barabasi_trust.png} & 
\includegraphics[scale=0.28]{fosiss_trust.png}
\end{tabular}
\caption{Strength of interactions distribution on different topologies. A. Random, Erd\"{o}s-R\'enyi network displays a normal-like
  distribution. B. Watts-Strogatz network strength of interactions distribution is bimodal and highly skewed to the right. C.
  Barab\'asi-Albert network strength of interactions distribution is also a normal-like curve. D. FOSISS, biomedical researchers
  collaboration network distribution of strength of interactions is skewed to
  the right.}\label{histo_trust}  
\end{figure}

@@

% For one-column wide figures use
%\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics{example.eps}
% figure caption is below the figure
%\caption{Please write your figure caption here}
%\label{fig:1}       % Give a unique label
%\end{figure}
%
% For two-column wide figures use
%\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
%\caption{Please write your figure caption here}
%\label{fig:2}       % Give a unique label
%\end{figure*}
%
% hello, friend
%
% For tables use
%\begin{table}
% table caption is above the table
%\section{%\caption{Please write your table caption here}}
%\label{tab:1}       % Give a unique label
% For LaTeX tables use
%\begin{tabular}{lll}
%\hline\noalign{\smallskip}
%first & second & third  \\
%\noalign{\smallskip}\hline\noalign{\smallskip}
%number & number & number \\
%number & number & number \\
%\noalign{\smallskip}\hline
%\end{tabular}
%\end{table}

>>>>

}

@@

\begin{figure} [h!]
\centering
\includegraphics[scale=0.5]{images/Fosiss_GC_final.png}
\caption{Bioemdical research collaboration network (FOSISS) giant component.}\label{Fosiss_GC}
\end{figure}

@@

\begin{figure} [h!]
\centering
\begin{tabular}{cc}
  \includegraphics[scale=0.28]{images/erdos_dc_nus_1.png} & \includegraphics[scale=0.28]{images/watts_dc_nus_1.png}
  \\
  \includegraphics[scale=0.28]{images/barabasi_dc_nus_1.png} & \includegraphics[scale=0.28]{images/fosiss_dc_nus_1.png}
\end{tabular}
\caption{Proportion of cooperators as a function of carrying capacity and time.}\label{CD}
\end{figure}

@@

\includegraphics[scale=0.28]{images/erdos_fitness_nus_1.png} & \includegraphics[scale=0.28]{watts_fitness_nus_1.png} \\
\includegraphics[scale=0.28]{images/barabasi_fitness_nus_1.png} & \includegraphics[scale=0.28]{fosiss_fitness_nus_1.png}
\end{tabular}
\caption{Utility $U$ dynamics as a function of carrying capacity $\nu$ and time.}\label{fitness}
\end{figure}

@@

\includegraphics[scale=0.28]{images/erdos_trust_nus_1.png} & \includegraphics[scale=0.28]{watts_trust_nus_1.png} \\
\includegraphics[scale=0.28]{images/barabasi_trust_nus_1.png} & \includegraphics[scale=0.28]{fosiss_trust_nus_1.png}
\end{tabular}
\caption{Strength of interactions $w$ dynamics as a function of carrying capacity $\nu$ and time.}\label{trust}
\end{figure}

@@

\includegraphics[scale=0.28]{images/erdos_state_nus.png} & \includegraphics[scale=0.28]{watts_state_nus.png} \\
\includegraphics[scale=0.28]{images/barabasi_state_nus.png} & \includegraphics[scale=0.28]{fosiss_state_nus.png}
\end{tabular}
\caption{Shifting population between cooperators and defectors as a function of
  carrying capacity $\nu$ and time.}\label{state} 
\end{figure}

@@

\includegraphics[scale=0.28]{images/erdos_fitness.png} & 
\includegraphics[scale=0.28]{images/watts_fitness.png} \\
\includegraphics[scale=0.28]{images/barabasi_fitness.png} & 
\includegraphics[scale=0.28]{images/fosiss_fitness.png}
\end{tabular}
\caption{Utility distribution on different topologies. A. Random,
  Erd\"{o}s-R\'enyi network displays a normal-like
  distribution. B. Watts-Strogatz network utility distribution is highly skewed
  to the right. C. Barab\'asi-Albert network. Utility is distributed highly
  skewed to the left. D. FOSISS, biomedical researchers collaboration network
  distribution of utility resembles to Barab\'asi-Albert
  network.}\label{histo_fitness} 
\end{figure}

@@

\includegraphics[scale=0.28]{images/erdos_trust.png} & 
\includegraphics[scale=0.28]{images/watts_trust.png} \\
\includegraphics[scale=0.28]{images/barabasi_trust.png} & 
\includegraphics[scale=0.28]{images/fosiss_trust.png}
\end{tabular}
\caption{Strength of interactions distribution on different topologies. A. Random, Erd\"{o}s-R\'enyi network displays a normal-like
  distribution. B. Watts-Strogatz network strength of interactions distribution is bimodal and highly skewed to the right. C.
  Barab\'asi-Albert network strength of interactions distribution is also a normal-like curve. D. FOSISS, biomedical researchers
  collaboration network distribution of strength of interactions is skewed to
  the right.}\label{histo_trust}  
\end{figure}

@@

% For one-column wide figures use
%\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics{images/example.eps}
% figure caption is below the figure
%\caption{Please write your figure caption here}
%\label{fig:1}       % Give a unique label
%\end{figure}
%
% For two-column wide figures use
%\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
%\caption{Please write your figure caption here}
%\label{fig:2}       % Give a unique label
%\end{figure*}
%
% hello, friend
%
% For tables use
%\begin{table}
% table caption is above the table
%\section{%\caption{Please write your table caption here}}
%\label{tab:1}       % Give a unique label
% For LaTeX tables use
%\begin{tabular}{lll}
%\hline\noalign{\smallskip}
%first & second & third  \\
%\noalign{\smallskip}\hline\noalign{\smallskip}
%number & number & number \\
%number & number & number \\
%\noalign{\smallskip}\hline
%\end{tabular}
%\end{table}
